Clean data

### 2023-05-08 analysis/01_experimental-design.Rmd
Confirming working with index-coded variables

@@

    smalldonors_criticized = fund1 * gov_rel2,
    smalldonors_crackdown = fund1 * gov_rel3,
    emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
    environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
    humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
    refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
    nottransp_criticized = transp1 * gov_rel2,
    nottransp_crackdown = transp1 * gov_rel3,
    nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
    nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
    nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
    nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
    nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
    nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
    nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
    nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
    nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
    nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
    nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
    nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
    nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
    nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
    nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
    nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
    nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
    nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
    nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
    nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
    nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
    nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,

>>>>

    # # Hypothesis 2b.
    # amnesty_criticized = org1 * gov_rel2,
    # greenpeace_criticized = org2 * gov_rel2,
    # oxfam_criticized = org3 * gov_rel2,
    # redcross_criticized = org4 * gov_rel2,
    # amnesty_crackdown = org1 * gov_rel3,
    # greenpeace_crackdown = org2 * gov_rel3,
    # oxfam_crackdown = org3 * gov_rel3,
    # redcross_crackdown = org4 * gov_rel3,

@@

    refugees_crackdown = issue4 * gov_rel3
    # # Hypothesis 4b.
    # wealthydonors_criticized = fund2 * gov_rel2,
    # govgrants_criticized = fund3 * gov_rel2,
    # wealthydonors_crackdown = fund2 * gov_rel3,
    # govgrants_crackdown = fund3 * gov_rel3,
    # # Hypothesis 4c.
    # emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
    # emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
    # environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
    # environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
    # humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
    # humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
    # refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
    # refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
    # # Hypothesis 5b.
    # transp_criticized = transp2 * gov_rel2,
    # transp_crackdown = transp2 * gov_rel3,
    # # Hypothesis 5c.
    # transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
    # transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
    # transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
    # transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
    # transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
    # transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
    # # Hypothesis 5d.
    # transp_emergency_criticized = transp2 * issue1 * gov_rel2,
    # transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
    # transp_environment_criticized = transp2 * issue2 * gov_rel2,
    # transp_environment_crackdown = transp2 * issue2 * gov_rel3,
    # transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
    # transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
    # transp_refugees_criticized = transp2 * issue4 * gov_rel2,
    # transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
    # # Hypothesis 5e.
    # transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
    # transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
    # transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
    # transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
    # transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
    # transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
    # transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
    # transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3

### 2023-05-08 analysis/02_clean-data.Rmd
Confirming working with index-coded variables

  # Reintroduce org1 and add the outside option coded as all zeros.
  for (n in 1:dim(dummy_X)[1]) {
    # Filter for respondent n.
    dummy_X_n <- dummy_design %>% filter(version == data$version[n])
    interactions_X_n <- dummy_interactions_design %>% filter(version == data$version[n])
    for (s in 1:dim(dummy_X)[2]) {
      # Filter for task s and include placeholder for org1.
      dummy_X_s <- dummy_X_n %>%
        filter(task == s) %>%
        mutate(org1 = 0) %>%
        select(org1, org2:gov_rel3)
      interactions_X_s <- interactions_X_n %>%
        filter(task == s) %>%
        mutate(org1 = 0) %>%
        select(org1, org2:transp_smalldonors_refugees_crackdown) # NOTE DIMENSIONS OF INTERACTIONS HARD-CODED.
      for (p in 1:(dim(dummy_X)[3]-1)) {
        # Filter for task s and alt p orgs.
        dummy_X_p <- dummy_X_n %>%
          filter(task == s, alt == p) %>%
          select(org2:org4) %>%
          as_vector()
        interactions_X_p <- interactions_X_n %>%
          filter(task == s, alt == p) %>%
          select(org2:org4) %>%
          as_vector()
        # Fill in org1 to complete org intercept.
        dummy_X_s[p, "org1"] <- ifelse(sum(dummy_X_p) == 1, 0, 1)
        interactions_X_s[p, "org1"] <- ifelse(sum(interactions_X_p) == 1, 0, 1)
      }
      # Save modified design, including outside option.
      dummy_X[n, s,,] <- rbind(dummy_X_s, rep(0, ncol(dummy_X_s))) %>% as.matrix()
      dummy_interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
    }
  }
}
if (index_coded == 1) {
  # Load the index-coded design.
  index_design <- read_csv(here::here("data", "derived_data", "index_design.csv")) %>%
    select(-`...1`) %>%
    rename(
      version = question_set,
      task = question,
      alt = choice
    )

@@

  # Add the outside option coded as all zeros (org1 and former reference levels already included).
  for (n in 1:dim(index_X)[1]) {
    # Filter for respondent n.
    index_X_n <- index_design %>% filter(version == data$version[n])
    interactions_X_n <- index_interactions_design %>% filter(version == data$version[n])
    for (s in 1:dim(index_X)[2]) {
      # Filter for task s.
      index_X_s <- index_X_n %>%
        filter(task == s) %>%
        select(org1:gov_rel3)
      interactions_X_s <- interactions_X_n %>%
        filter(task == s) %>%
        select(org1:transp_smalldonors_refugees_crackdown) # NOTE DIMENSIONS OF INTERACTIONS HARD-CODED.
      # Save modified design, including outside option.
      index_X[n, s,,] <- rbind(index_X_s, rep(0, ncol(index_X_s))) %>% as.matrix()
      index_interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
    }
  }
}
```

>>>>

  # Reintroduce org1 and add the outside option coded as all zeros.
  for (n in 1:dim(dummy_X)[1]) {
    # Filter for respondent n.
    dummy_X_n <- dummy_design %>% filter(version == data$version[n])
    interactions_X_n <- dummy_interactions_design %>% filter(version == data$version[n])
    for (s in 1:dim(dummy_X)[2]) {
      # Filter for task s and include placeholder for org1.
      dummy_X_s <- dummy_X_n %>%
        filter(task == s) %>%
        mutate(org1 = 0) %>%
        select(org1, org2:gov_rel3)
      interactions_X_s <- interactions_X_n %>%
        filter(task == s) %>%
        mutate(org1 = 0) %>%
        # select(org1, org2:transp_smalldonors_refugees_crackdown) # HARD-CODED
        select(org1, which(names(interactions_X_n) == "org2"):ncol(interactions_X_n))
      for (p in 1:(dim(dummy_X)[3]-1)) {
        # Filter for task s and alt p orgs.
        dummy_X_p <- dummy_X_n %>%
          filter(task == s, alt == p) %>%
          select(org2:org4) %>%
          as_vector()
        interactions_X_p <- interactions_X_n %>%
          filter(task == s, alt == p) %>%
          select(org2:org4) %>%
          as_vector()
        # Fill in org1 to complete org intercept.
        dummy_X_s[p, "org1"] <- ifelse(sum(dummy_X_p) == 1, 0, 1)
        interactions_X_s[p, "org1"] <- ifelse(sum(interactions_X_p) == 1, 0, 1)
      }
      # Save modified design, including outside option.
      dummy_X[n, s,,] <- rbind(dummy_X_s, rep(0, ncol(dummy_X_s))) %>% as.matrix()
      dummy_interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
    }
  }
}
if (index_coded == 1) {
  # Load the index-coded design.
  index_design <- read_csv(here::here("data", "derived_data", "index_design.csv")) %>%
    select(-`...1`) %>%
    rename(
      version = question_set,
      task = question,
      alt = choice
    )

@@

  # Add the outside option coded as all zeros (org1 and former reference levels already included).
  for (n in 1:dim(index_X)[1]) {
    # Filter for respondent n.
    index_X_n <- index_design %>% filter(version == data$version[n])
    interactions_X_n <- index_interactions_design %>% filter(version == data$version[n])
    for (s in 1:dim(index_X)[2]) {
      # Filter for task s.
      index_X_s <- index_X_n %>%
        filter(task == s) %>%
        select(org1:gov_rel3)
      interactions_X_s <- interactions_X_n %>%
        filter(task == s) %>%
        # select(org1:transp_smalldonors_refugees_crackdown) # HARD-CODED
        select(which(names(interactions_X_n) == "org1"):ncol(interactions_X_n))
      # Save modified design, including outside option.
      index_X[n, s,,] <- rbind(index_X_s, rep(0, ncol(index_X_s))) %>% as.matrix()
      index_interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
    }
  }
}
```
